Rice yield improvements by plant breeding are offset by decreases over time

### 2017-05-04 output/breed_paper.Rnw
Changes

@
\caption{The performance of two major cultivars at the CA Rice
  Experiment Station (RES) over the period 1995 -- 2015. The line is the average
  yield for each cultivar over the period which it was planted at the
  RES. The newer cultivar, M-206, appears to have a slight yield
  advantage over the older cultivar, M-202.}
\label{fig:compare_yrs}
\end{figure}

@@

As seen in Fig. \ref{fig:yrs}, there is a small decrease in yield
over time once a cultivar is released, though the estimated effect is
small compared to the variability in the data set. This decrease is estimated to be
\Sexpr{round(fixef(RES_yrs_fit)[2] * scl, 1)} lbs
year\textsuperscript{-1}. The oldest cultivar in the trials has lost
an estimated \Sexpr{round(fixef(RES_yrs_fit)[2] * scl * 36 , 1)} kg ha\textsuperscript{-1} since release. Using just data from the Rice
Experiment Station (RES), the estimated effect is more drastic
(an estimated \Sexpr{round(fixef(RES_yrs_fit)[2] * scl , 1)} kg
ha\textsuperscript{-1} year\textsuperscript{-1}), but with a wider credible interval
(\Sexpr{RES_CI[1]} -- \Sexpr{RES_CI[2]} vs \Sexpr{all_CI[1]} --
\Sexpr{all_CI[2]}).

@@

@
\caption{The performance of two major cultivars at the CA Rice
  Experiment Station (RES) since the year each cultivar was
  released. Both M-202 ($\bullet$) and M-206 ($\blacktriangle$) have similar
  intercepts, suggesting similar yield at the time of release and an
  apparent yield advantage of the newer cultivar, M-206, might be
  explained by a yield loss of M-202 over time. Points represent the
  mean, and bars (|) the standard error.}
\label{fig:res_since_release}
\end{figure}

>>>>

@
\caption{The performance of two major cultivars at the CA Rice
  Experiment Station (RES) over the period 1995 -- 2015. The line is the average
  yield for each cultivar over the period which it was planted at the
  RES. The newer cultivar, M-206, appears to have a slight yield
  advantage (an estimated \Sexpr{m202_v_206[2]} kg ha\textsuperscript{-1})over the older cultivar, M-202.}
\label{fig:compare_yrs}
\end{figure}

@@

When yields are arranged according to the years since release, there
is a small decrease in yield over time once a cultivar is released,
though the estimated effect is small compared to the variability in
the data set. This decrease is estimated to be
\Sexpr{round(fixef(RES_yrs_fit)[2] * scl, 1)} kg
ha\textsuperscript{-1} year\textsuperscript{-1} (90\% CI: \Sexpr{RES_CI[2]} --
\Sexpr{RES_CI[1]}). The oldest cultivar
in the trials is estimated to have lost
\Sexpr{round(fixef(RES_yrs_fit)[2] * scl * 36 , 1)} kg
ha\textsuperscript{-1} since release.

Again comparing the yield of two prominant cultivars, M-202 and M-206,
arranged not by the year but rather the years since release, we find
that the two cultivars are compariable and that the estimated yield
advantage (\Sexpr{m202_v_206[2]} kg ha\textsuperscript{-1}) can be
explained by the differences in the amount of time that has passed
since each cultivar was released
(Fig. \ref{fig:compare_since_release})

@@

@
\caption{The performance of two major cultivars at the CA Rice
  Experiment Station (RES) since the year each cultivar was
  released. Both M-202 ($\bullet$) and M-206 ($\blacktriangle$) have similar
  intercepts, suggesting similar yield at the time of release and an
  apparent yield advantage of the newer cultivar, M-206, might be
  explained by a yield loss of M-202 over time. Points represent the
  mean, and bars (|) the standard error.}
\label{fig:compare_since_release}
\end{figure}
